\chapter{Testing}


\section{Introduction}\\
Testing is a process of executing error. It is an important and critical stage in software development. It plays an important role in determining the quality and reliability of the application. With this process, several test cases are devised. A test case means a set of data that the system will process as the normal input. Testing also adds value to the product by conforming the user requirements. Testing verifies that this software deliverable conforms precisely to the functional and design specification that have been compiled during analysis and design phases. A good test case is one that has a high portability of finding an undiscovered error. Testing involves a series of operation of a system or application under controlled conditions and subsequently evaluating results. The controller conditions should include both normal and abnormal conditions. It is planned and monitors for each testing level.

% Testing is a process of executing error. A good test is the ......\\ 
%  The increasing  a software failure are motivating forces for well planned, through testing...........\\

% This section type your project contents 

\section{White Box Testing}
This testing reveals the internal working of the code i.e. each of the programming elements is exercised properly. The white box testing for the proposed system focus on the program control structure and it is also called clear box testing. Test cases for the proposed system are designed to ensure that all statements in the program have executed at least once during testing and that all logical conditions have been exercised. White box testing is small implying that this test is typically applied to small program components.




% This section type your project contents 

\section{Black Box Testing}
Black Box Testing was conducted to ensure the MatricsV dashboard met functional requirements without examining internal code. The testing focused on input-output validation, such as verifying that charts updated correctly with filters, views rendered properly, and the interface was responsive across devices. Key scenarios included testing chart behavior, data filtering, error handling, and navigation. For example, applying a date filter correctly updated all relevant charts, while mobile view tests ensured proper layout adjustments. Issues like stale chart props and overflow bugs were identified and resolved. This testing approach ensured a smooth, user-focused experience and reliable functionality across different environments.


% This section type your project contents 


\section{Validation Testing}
Validation Testing was performed to ensure the MatricsV dashboard met all specified requirements and user expectations. Each feature, including data visualization, filtering, responsiveness, and navigation, was verified against the original project scope. Charts were tested with dynamic datasets to confirm accurate rendering, and filters were validated for correct interaction. Responsive design was checked across devices to ensure consistent usability. The final product successfully passed all validation checks, confirming it aligned with the intended functionality and design. This process guaranteed that the application not only worked correctly but also delivered a user-centric and purpose-driven experience.

% This section type your project contents 

\section{GUI Testing}
GUI Testing was conducted to ensure the visual elements of the MatricsV dashboard functioned correctly and provided a seamless user experience. All user interface components—charts, filters, dropdowns, date pickers, and navigation tabs—were tested for proper alignment, styling, responsiveness, and interactivity. Tailwind CSS utilities were verified across screen sizes to confirm consistent design. Focus was placed on color schemes, font consistency, hover effects, and button functionality. Interactive elements responded accurately to user actions without layout shifts or overlap issues. The testing confirmed that the dashboard maintained both aesthetic quality and usability across different browsers and devices.



% This section type your project contents 