\chapter{Proposed System}


\section{Proposed System}
% helps to manage critical processes in Hospital.\\
% \textbf{Patient Registration:} 
%  It provides scheduling/Canceling/Rescheduling of appointments appointment schedule of doctors.\\
% % This section type your project contents 

The proposed system, MatricsV, is designed to provide a modern solution for visualizing complex data through an interactive dashboard. It is user-friendly, scalable, and helps stakeholders easily understand trends and insights. With responsive design, dynamic charts, and real-time filtering, the system meets the needs of both developers and end-users. MatricsV not only enhances data representation but also ensures better performance and usability. The aim of the proposed system is to improve data interpretation and decision-making. It reduces manual effort, ensures efficient data handling, and overcomes the limitations of traditional static dashboards, making data analysis smarter and more accessible.


% \textbf{My Assistant:}
%  My Assistant as a utility performs the role of a personal assistant., It stores information .\\
% % This section type your project contents 



\section{User Privileges}
% The user type determines the privileges that the user has within EHMS.\\

% % This section type your project contents 

\section*{User Privileges}

The proposed system defines clear user privileges to ensure secure and efficient access control within the dashboard environment. Each user role is granted specific rights based on their level of interaction with the system.

\begin{itemize}
    \item \textbf{Admin:}
    \begin{itemize}
        \item Full access to all dashboard features
        \item Manage data sources and chart configurations
        \item Control user access and roles
        \item Perform system-level configurations and updates
    \end{itemize}
    
    \item \textbf{Regular User:}
    \begin{itemize}
        \item View and interact with charts and visualizations
        \item Apply filters and export data
        \item Access assigned datasets and reports
    \end{itemize}
    
    \item \textbf{Guest User (Optional):}
    \begin{itemize}
        \item Limited access to publicly available data views
        \item Read-only access without personalization features
    \end{itemize}
\end{itemize}

These roles ensure data integrity, streamline operations, and maintain security by restricting sensitive functions to authorized users only.


\section{Objective of the System}
% This section type your project contents 

% \begin{itemize}
% \item Latest technology 
% \item Graphical user Interface

The main objective of the system is to develop an interactive and responsive data visualization dashboard that simplifies complex data interpretation. The system aims to provide users with real-time insights through visually intuitive charts and graphs. It is designed to enhance decision-making by presenting data in an organized and accessible manner. Additionally, the system focuses on delivering a seamless user experience across devices, reducing manual effort, and ensuring performance and scalability. Overall, the goal is to bridge the gap between raw data and actionable insights using modern web technologies
\end{itemize}